Efficient pedigree recording for fast population genetics simulation

### 2017-11-27 forwards_paper.tex
add methods for benchmarking

\plr{Jaime and Kevin to describe simulation methods here (separately).}

Comparison of simulation with/without msprime, using \simupop{}
or maybe just a simple haploid simulation with 1000 QTL and stabilizing selection on a trait (say).

Maybe an estimate of how long \emph{just} the ARG recording and simplification takes,
so that then we can say how fast the simulator would have to be to do $10^6$ whole chromosomes for $10^7$ generations
in a day.

>>>>

To measure the performance gains from ancestry recording, we ran simulations implemented in C++ (see above) with and
without ancestry tracking.  The simulations without ancestry tracking introduced neutral mutations at a scaled mutation
rate equal to the scaled recombination rate (\textit{e.g.}, $\theta = 4N\mu = \rho$, where $\rho = 4Nr$, $N$ is the
diploid population size, $\mu$ is the
mutation rate to neutral mutations (per gamete, per generation) and $r$ is the recombination rate per diploid per
generation.  Both $\mu$ and $r$ are the means of a Poisson process and we used the infinitely-many sites mutation model
\citep{Kimura1969-uc}.

We varied $N \in (1000, 10000, 50000)$, $\rho \in (10^3, 10^4, 10^5)$ and ran a single replicate of all $(N,\rho)$
combinations.  Deleterious mutations were introduced at rate $\rho/100$ per generation, drawing scaled selection
coefficients ($2Ns$)
from a Gamma distribution with a mean of -5 and a shape parameter of 1.  This distribution of fitness effects results in
thousands of weakly-deleterious mutations segregating in the population, many of which drift to intermediate
frequencies.

We ran all benchmarks on an Ubuntu Linux (version 16.04) system with two 2.6 Gigahertz Intel E5-2650 CPU with
hyperthreading enabled.  We ran one simulation at a time and the machine was under minimal load otherwise.  We used GNU
parallel \citep{Tange2011a} to kill
any simulation that did not finish within 72 hours.  We used the Linux \texttt{time} command to record run time and peak
memory usage of each replicate and our simulation scripts separately recorded the time spent in various steps of each
run.

For efficiency reasons, we only ran \simupop{} with ancestry tracking.

\krt{Jaime--any details here to add re: how simuPOP was tweaked??}

% \plr{Jaime and Kevin to describe simulation methods here (separately).}
% 
% Comparison of simulation with/without msprime, using \simupop{}
% or maybe just a simple haploid simulation with 1000 QTL and stabilizing selection on a trait (say).
% 
% Maybe an estimate of how long \emph{just} the ARG recording and simplification takes,
% so that then we can say how fast the simulator would have to be to do $10^6$ whole chromosomes for $10^7$ generations
% in a day.
